Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-28 Manuscript_draft.Rmd
Formatting Q1 plot

#change clusters to descriptions
asymptomaticQ1$label[asymptomaticQ1$label == "#4479 Harada [cluster:1]"] <- "#4479 Harada [Patients]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4479 Harada [cluster:2]"] <- "#4479 Harada [Healthcare workers]"
#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:1]"] <- "#2826 Taylor []" #clarify
#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:2]"] <- "#2826 Taylor []"
asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly [cluster:1]"] <- "#2892 Kennelly [Nursing home residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly [cluster:2]"] <- "#2892 Kennelly [Nursing home staff]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul [cluster:1]"] <- "#4968 van Buul [Nursing home residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul [cluster:2]"] <- "#4968 van Buul [Healthcare workers]"
asymptomaticQ1$label[asymptomaticQ1$label == "#5273 Theuring [cluster:1]"] <- "#5273 Theuring [School students and staff]"
asymptomaticQ1$label[asymptomaticQ1$label == "#5273 Theuring [cluster:2]"] <- "#5273 Theuring [Household members]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2751 van den Besselaar [cluster:1]"] <- "#2751 van den Besselaar [Healthcare workers]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2751 van den Besselaar [cluster:2]"] <- "#2751 van den Besselaar [Residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:1]"] <- "#2826 Taylor [Healthcare personnel]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:2]"] <- "#2826 Taylor [Residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#3719 Ladhani [cluster:1]"] <- "#3719 Ladhani [Residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#3719 Ladhani [cluster:2]"] <- "#3719 Ladhani [Healthcare workers]"
asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:1]"] <- "#5551 Vohra [Presurgical patients]"
asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:2]"] <- "#5551 Vohra [Undergoing chemotherapy]"
asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:1]"] <- "#6526 Garibaldi [Residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:2]"] <- "#6526 Garibaldi [Staff]"

@@

#sort by standard error
#read meta book and figure it out
#same as precision plot
pdf(file = 'forest_meta_Q1.pdf', width = 10, height = 30)

>>>>

#change clusters to descriptions
asymptomaticQ1$label[asymptomaticQ1$label == "#4479 Harada S [cluster:1]"] <- "#4479 Harada S [Patients]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4479 Harada S [cluster:2]"] <- "#4479 Harada S [Healthcare workers]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly SP [cluster:1]"] <- "#2892 Kennelly SP [Nursing home residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly SP [cluster:2]"] <- "#2892 Kennelly SP [Nursing home staff]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul LW [cluster:1]"] <- "#4968 van Buul LW [Nursing home residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul LW [cluster:2]"] <- "#4968 van Buul LW [Healthcare workers]"
asymptomaticQ1$label[asymptomaticQ1$label == "#9442 Theuring S [cluster:1]"] <- "#9442 Theuring S [School students and staff]"
asymptomaticQ1$label[asymptomaticQ1$label == "#9442 Theuring S [cluster:2]"] <- "#9442 Theuring S [Household members]"
asymptomaticQ1$label[asymptomaticQ1$label == "#7465 van den Besselaar JH [cluster:1]"] <- "#7465 van den Besselaar JH [Healthcare workers]"
asymptomaticQ1$label[asymptomaticQ1$label == "#7465 van den Besselaar JH [cluster:2]"] <- "#7465 van den Besselaar JH [Residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor J [cluster:1]"] <- "#2826 Taylor J [Healthcare personnel]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor J [cluster:2]"] <- "#2826 Taylor J [Residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#3719 Ladhani SN [cluster:1]"] <- "#3719 Ladhani SN [Residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#3719 Ladhani SN [cluster:2]"] <- "#3719 Ladhani SN [Healthcare workers]"
#asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:1]"] <- "#5551 Vohra [Presurgical patients]"
#asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:2]"] <- "#5551 Vohra [Undergoing chemotherapy]"
#asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:1]"] <- "#6526 Garibaldi [Residents]"
#asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:2]"] <- "#6526 Garibaldi [Staff]"

@@

#sort by standard error
#read meta book and figure it out
#same as precision plot
pdf(file = 'forest_meta_Q1.pdf', width = 10, height = 28)
